---
name: Shira
surname: Salingre
position: "Marine Ecologist | Data Analyst"
email: "shira.salin@gmail.com"
www: shirasal.github.io
github: shirasal
linkedin: shira-salingre
output: 
  vitae::latexcv:
    theme: classic
---


```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE, warning = FALSE, message = FALSE)
library(vitae)
```

## Professional Experience

### Marine ecology specialist
_Song of the Sea (Self employed) \| 2015 - Present_

**Professional adviser and project coordinator** for a multitude of projects, mainly focusing on creating educational and professional materials on marine ecology and conservation.\
[Example: NPA (Nature and Parks Authority) posters for the general public on marine fauna, in Hebrew](https://www.parks.org.il/article/%d7%9b%d7%a8%d7%96%d7%95%d7%aa-%d7%99%d7%9e%d7%99%d7%95%d7%aa/)

**Data analyst** in various ecological research projects.

### Projects ecologist
_HaMaarag - Israel's Nature Assessment Program \| 2020 - 2022_

Ecological data processing, analysis, visualisation and reporting for the nonprofit organisation [Hamaarag](https://hamaarag.org.il/). Worked as part of the team of the [State of Nature Report 2022](https://hamaarag.org.il/report/%d7%93%d7%95%d7%97-%d7%9e%d7%a6%d7%91-%d7%94%d7%98%d7%91%d7%a2-2022/), and other projects.

### Teaching assistant in BSc course
_Ruppin Academic Center \| 2019 - 2022_

Teaching undergraduate students in an intensive week-long course on the ecology of the Mediterranean.

### Marine ecology MSc student and researcher
_The Belmaker lab, Tel Aviv University \| 2018-2020_

Explored how co-occurrence of fish species in the Mediterranean sea changes along environmental gradients. My whole work was based on using models in R environment.

My dataset: [MEData](https://belmaker-lab.github.io/medata/)

### Nature conservation tour guide
_Nature and Parks Authority \| 2007-2019_

Guided tours that were nature conservation orientated, in field trips and in class or lectures. Lead long-term ecological and environmental educational projects.

### Elasmobranch researcher
_Sharks in Israel \| 2014-2019_

Established and managed a shark and rays citizen science observation database. Co-founder of the organisation ["Sharks in Israel"](https://www.sharks.org.il/main/).

### Recreational fishing surveyor
_Nature and Parks Authority & Tel Aviv University \| 2016-2018_

Collected data from recreational fishermen on their fishing habits and catch to create first-ever quantitative estimates on recreational fishing extent in Israel.

### Junior research assistant
_Gitai Yahel's lab, Ruppin Academic Center \| 2016-2018_

Worked on various ecological project as part of the [Ruppin Estuarine Coastal Observatory (RECO)](https://www.ruppin.ac.il/en/Gitai-Yahel-Lab/Pages/default.aspx). Here I took samples from the estuary, extracted biological and chemical information from them and assisted with other projects on marine ascidians.

### Sea turtle hatching season volunteer coordinator
_The National Sea Turtle Rescue Center, NPA \| 2011 and 2017_

Coordinated and managed a team of volunteers of the Sharon region hatchery, throughout the hatching season. As part of my work I also had to update and consult the hatching database for our operations.

### Sea turtle care taker volunteer
_The National Sea Turtle Rescue Center, NPA \| 2009-2016_

Cleaned and fed turtles and helped when needed in medical operations. It was great fun!

### Invasive sea star removal volunteer
_Earthcare St. Kilda, Melbourne, Australia \| 2013_

A one off volunteer experience I had while living and working in Melbourne, Australia. We were physically removing northern pacific seastar from Port Phillip bay.

### Humpback whale research volunteer
_Eye of the Whale, Alaska, USA \| 2011_

While traveling in Alaska I took part in this unique research where we recorded humpback whales in the bay of Homer, and identified the individuals. It was an amazing experiance I will never forget.


## Education

```{r}
library(tibble)
tribble(
  ~ Degree, ~ Year, ~ Institution, 
  "Master of Science (Ecology)", "2018-2020", "Tel Aviv University", 
  "Bachelor of Science (Marine Sciences)", "2014-2017", "Ruppin Academic Center", 
) %>% 
  detailed_entries(Degree, Year, Institution)
```

In my BSc I learned basics of research methods, including data analysis using GIS software and Microsoft Excel. My studies included a research project on the effects of fish farms in open seas.

During my Masters studies I learned and practiced most of my data science skills, mainly using R, Rstudio (now 'posit') and GitHub. I also started a Github account for our lab, initiated a Google website platform for our fish identification guide (which we all built together), gathered and cleaned our Mediterranean database and lead lab hackathons. My research topic was "Dynamic fish networks along environmental gradients in the Mediterranean Sea".



## Skills

### Data processing, analysis and visualisation
-   **R language, RStudio, Rmarkdown**.
-   Spreadsheet softwares: **Microsoft Excel, Google Sheets**.
-   Geographical information systems (**GIS**): qGIS, ArcGIS.
-   **GitHub** repositories, version control and collaboration tools
-   Basic understanding of **SQL**
-   Data analysis with **Python** (namely pandas library)

### Science communication
-   Public speaking
-   Presentations creation (**Microsoft PowerPoint**, **Google Slides**, **RMarkdown**)
-   Article writing (blog posts, popular science)
-   Scientific report writing

### Natural languages
-   English: proficient, fluent.
-   Hebrew: native.
-   Spanish (Castellano): beginner (B1).

```{r include=FALSE}
# From the original template
tribble(
  ~Year, ~Type, ~Desc,
  1903, "Physics", "Awarded for her work on radioactivity with Pierre Curie and Henri Becquerel",
  1911, "Chemistry", "Awarded for the discovery of radium and polonium"
) %>% 
  brief_entries(
    glue::glue("Nobel Prize in {Type}"),
    Year, 
    Desc
  )
```


\fancyfoot[CO,CE]{
  \textcolor{gray}{
    This CV was built with the [vitae](https://github.com/mitchelloharawild/vitae) package.
    }
  }